---
title: " Monash Master of Data Science"
author: "Emi Tanaka"
date: "`r Sys.Date()`"
format: 
  html: 
    code-fold: false
---


```{r setup, include = FALSE}
library(tidyverse)
library(visNetwork)
library(rvest)
library(RSelenium)
library(glue)
library(tidytext)
knitr::opts_chunk$set(echo = FALSE,
                      cache = TRUE,
                      cache.path = "cache/",
                      fig.path = "images/")

```


## Monash

### Units

The directed graph below shows the units in the Master of Data Science as nodes with edges showing the subject that is a prerequisite for the unit. The node that the arrow is pointing to requires the unit that is linked.

```{r monash}
rD <- rsDriver(browser="firefox", port=4790L, verbose=F)
remDr <- rD[["client"]]

# "C6009" is the Indonesian campus version
code <- "C6004"
baseurl <- "https://handbook.monash.edu"
year <- 2022
wait_time <- function() Sys.sleep(sample(3:5, 1))

remDr$navigate(glue("{baseurl}/2022/courses/{code}"))
course_html <- read_html(remDr$getPageSource()[[1]])

title <- course_html %>% 
  html_element("h2") %>% 
  html_text() %>% 
  str_replace(paste0(code, " - "), "")

curriculum <- course_html %>% 
  html_element("#curriculumStructure") %>% 
  html_element(".css-to4w00-Box") %>% 
  html_elements("a") %>% 
  html_attr("href")

data <- map_dfr(curriculum, function(unit) {
      cunit <- str_replace(unit, paste0("/", year, "/units/"), "")
      remDr$navigate(glue("{baseurl}{unit}"))
      wait_time()
      unit_html <- read_html(remDr$getPageSource()[[1]])
      subject_text <- unit_html %>% 
        html_element("h2") %>% 
        html_text() 
    
      reqs <- unit_html %>% 
        html_element("#requisites") 
      
      if(length(reqs)) {
        reqs <- reqs %>% 
          html_element(".css-to4w00-Box") %>% 
          html_children()
      }
      
      reqs_list <- list()
      for(areq in reqs) {
        area <- areq %>% 
          html_element("strong") %>% 
          html_text()
        reqs_list[[area]] <- areq %>% 
          html_elements("a") %>% 
          html_attr("href") %>% 
          list()
      }
      
      overviews <- unit_html %>% 
        html_element("#Overview") %>% 
        html_element(".OverviewInner") %>% 
        html_elements("div") %>% 
        html_text() %>% 
        pluck(2)
      
      outcomes <- unit_html %>% 
        html_elements("#Learningoutcomes .AccordionItem") %>%
        html_text() %>% 
        str_replace("^[0-9]+[.]", "") %>%
        str_replace("keyboard_arrow_down$", "")
      message(glue::glue("{cunit} done!"))
      tibble(!!!c(list(Course = title, 
                       Course_code = code, 
                       Unit_code = cunit,
                       Unit = subject_text,
                       Overview = overviews,
                       Outcomes = list(outcomes)), 
                       reqs_list))
})

data %>% 
  rowwise() %>% 
  mutate(Outcomes = paste(Outcomes, collapse = "| "),
         Prohibition = paste(Prohibition, collapse = ", "),
         Prerequisite = paste(Prerequisite, collapse = ", "),
         Corequisite = paste(Corequisite, collapse = ", ")) %>% 
  mutate(across(c(Prohibition, Prerequisite, Corequisite), 
               ~ifelse(is.na(.x), 
                       "", 
                       str_replace_all(.x, glue::glue("/{year}/units/"), "")))) %>% 
  write_csv(file = "data/monash-master-datasci.csv")
```


Note: zoom in to see the labels of the nodes and hover over the node to see the full name (available only for core units for now).



```{r}
nodes_incomplete <- data %>% 
  filter(Course_code == "C6004") %>% 
  mutate(Unit = str_replace(Unit, paste0(Unit_code, " - "), "")) %>% 
  select(label = Unit_code, title = Unit) %>% 
  select(label, title)


cat(data$Course[1])

edges_name <- data %>% 
  unnest_longer(Prerequisite) %>% 
  mutate(Prerequisite = str_replace(Prerequisite, "/2022/units/", "")) %>% 
  select(to = Unit_code, from = Prerequisite) %>% 
  filter(!is.na(from)) 

missing_nodes <- setdiff(c(edges_name$from, edges_name$to), nodes_incomplete$label)

nodes <- nodes_incomplete %>% 
  add_row(label = missing_nodes) %>% 
  mutate(id = 1:n())

edges <- edges_name %>% 
  mutate(from = match(from, nodes$label),
         to = match(to, nodes$label))

visNetwork(nodes, edges, width = "100%") %>% 
  visEdges(arrows = "to")
```
### Text analysis

Below is a bigram and trigram of the overview description for units in the Monash Master of Data Science. (It's not that insightful.)

```{r, message = FALSE, warning = FALSE}
ngram <- 3
data %>% 
  filter(Course_code == "C6004") %>%
  unnest_tokens(word, Overview, token = "ngrams", n = ngram, n_min = 2) %>% 
  separate(word, c("word1", "word2", "word3"), sep = " ") %>% 
  filter(if_all(num_range("word", c(1,ngram)), 
              ~!str_detect(., paste0(paste0("^", stop_words$word, "$"), collapse = "|")))) %>% 
  select(starts_with("word")) %>% 
  mutate(word = str_c(word1, word2, word3, sep = " ")) %>% 
  count(word, sort = TRUE) %>% 
  filter(n > 2) %>% 
  knitr::kable() %>% 
  kableExtra::kable_classic()
```


